The analogue method for precipitation prediction: finding better analogue situations at a sub-daily time step

### 2017-03-31 Moving temporal window - HESS/template.tex
HESS corrections.

	The	Analogue method (AM) is based on the hypothesis that two relatively similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}. It is a statistical downscaling methods \citep{Maraun2010} and consist of finding past situations that are similar to the target day of interest in terms of the atmospheric circulation or other synoptic predictors. The local weather variables of interest (predictand) that were observed at the analogue dates are used to construct a probabilistic prediction for the target day \citep{Duband1970, Zorita1999}. Multiple variations of the method exist \citep[a non-exhaustive listing can be found in][]{BenDaoud2016}. The AMs are used for operational precipitation forecasting, either in the context of weather forecasting, flood forecasting, or hydropower production \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Desaint2008a, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012, Obled2014, Hamill2015, BenDaoud2016}, as well as for precipitation downscaling from a climate perspective \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015}. Other applications focus on temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, and solar power \citep{Alessandrini2015a, Bessa2015}. AMs can provide multivariate predictions that are physically consistent \citep{Raynaud2016b}. Their spatial transferability is analysed in \citet{Chardon2014} and \citet{Radanovics2013}. Their temporal transferability has also been the topic of recent studies for past or future climates \citep{Dayon2015, Caillouet2016}.

	The method requires two different archives. The first is a meteorological archive describing the state of the atmosphere at a synoptic scale, such as reanalysis datasets. The second is an archive of the target variable to be predicted, here precipitation. This archive is made of precipitation cumulated over a certain time duration, most often daily but sometimes sub-daily, either at a target station or integrated over a target catchment. Obviously, the period to be used is limited to the smallest period common to the two archives.

@@

	One can question the interest of using moving daily totals when 6-hourly precipitation series can be predicted instead. However, the 6-hourly time series generated by the AM might not represent accurately the intra-daily precipitation distribution. In addition, sometimes a resolution finer than the daily time step is not needed and another disaggregation technique may be used afterwards. Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact than 24h daily totals.

	The MTW finds analogue situations at different hours of the day, which can also be seen as an inflation of the archive length. However, despite having $x$ time more candidate situations, the quantity of new information is not expected to be as important as a $x$ time longer archive due to significant correlation between successive situations within the same day. Nevertheless, if the MTW can improve the prediction skill of the AM, it means that it does extract new information from the archive.

@@

	Synoptic-scale variables, used as predictors, were extracted from two of the most recent global reanalysis datasets: the european ERA-20C \citep{Poli2016} with a 3h temporal resolution, and a spatial resolution of 1\textdegree, and MERRA-2, from NASA, with a 6h temporal resolution and a spatial resolution of 0.625\textdegree x 0.5\textdegree. The study was originally performed on the NCEP/NCAR reanalysis 1 dataset \citep{Kalnay1996}, and the conclusions were similar. ERA-20C is build by assimilating only surface observations, and is thus available on a long period (1900\textendash 2010). On the contrary, MERRA-2 is build by assimilating observations at higher levels and from more sensors, including satellite data, but is then more limited in time (1980\textendash present). It is of interest to assess the relevance of an MTW with these two datasets, as they represent different kind of products. The specific advantages of ERA-20C is that it allows testing an MTW with a 3h time step, and it covers a long period. On the other hand, MERRA-2 has a higher spatial resolution and can be expected to be more correct at higher levels of the atmosphere. The variables extracted from these datasets are geopotential heights at 500~hPa (Z500) and 1000~hPa (Z1000), as well as the total precipitable water (TPW) and the relative humidity at 850~hPa (RH850).

@@

	The first considered AM is based on the analogy of the atmospheric circulation only \citep[Table \ref{table:method_2Z},][]{Obled2002, Bontron2005}. Searching for analogue situations to a target day starts by a seasonal stratification through a preselection step of the potential candidates for analogy. The restriction is a search for analogue days within a 4-month window centred on the target date for every year of the archive. The similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score (S1) that is a comparison of gradients on geopotential heights over a certain spatial window and at certain hours:

@@

	The second reference method (2Z-2MI, Table \ref{table:method_2Z-2MI}) adds a subsequent level of analogy with moisture variables, compared by means of the root-mean-square error (RMSE):

@@

	AMs rely on parameters that need to be defined for every level of analogy. Here, the selection of the meteorological variables used as predictors, as well as their corresponding analogy criteria, pressure level, and hour of the day will be identical to the methods 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) described above. The parameters that are here calibrated are:

@@

	The semi-automatic sequential procedure elaborated by \citet{Bontron2004} was used to calibrate the AM \cite[see also ][]{Radanovics2013, BenDaoud2016}. The analogy levels (e.g. the atmospheric circulation or moisture index) are calibrated sequentially. The parameters calibrated by this approach, for every level of analogy, are the spatial windows on which the predictors are compared and the number of analogues. The procedure, as defined by \citet{Bontron2004}, consists of the following steps:

	\begin{enumerate}
		\item For every level of analogy:
		\begin{enumerate}
			\item Identification of the most skilled unitary cell (one point for moisture variables and four for geopotential heights in order to process the gradients) over a large domain. Every point (or cell) of the full domain is assessed on all predictors of the level of analogy, jointly (consisting generally of the same variable but on different pressure levels and at different hours).
			\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain. The spatial window grows by repeating the previous steps until no improvement is reached.
			\item The number of analogue situations $N_{1}$, which was initially set at an arbitrary value, is then reconsidered and optimized for the current level of analogy.
		\end{enumerate}
		\item A new level of analogy can then be added, based on other variables (such as the moisture index) at chosen pressure levels and hours of the day. The number of analogues for the next level of analogy, $N_{2}$, is initiated at a chosen value. The procedure starts again from step 1 (calibration of the spatial window and the number of analogues) for the new level. The parameters calibrated on the previous analogy levels are fixed and do not change. 
		\item Finally, the numbers of analogues $N_{1}$ and $N_{2}$ for the different levels of analogy are reassessed. This is done iteratively by varying the number of analogues of each level in a systematic way.
	\end{enumerate}

@@

	The 29-yr hourly precipitation dataset was divided into a calibration period (CP) and a validation period (VP), in order to assess the robustness of the proposed improvements on independent data. The selection of the VP was evenly distributed over the entire series \citep{BenDaoud2010} to reduce potential biases related to trends linked to climate change or to the evolution in measurement techniques. Thus, one out of every five years was selected for validation, which represents a total of 6 years for the VP and 23 for the CP.

@@

	The moving time window (MTW) technique aims at finding better analogue situations at different hours of the day rather than comparing the predictors at the same fixed hours. The target situation (the day to predict) is still the same as in the conventional approach, that is a daily precipitation total between 06:00 and 30:00~UTC, characterized by predictors which are e.g. Z1000 and Z500 at 12:00 and 24:00~UTC respectively. The difference is that candidate situations are not only considered at the same time (e.g. 12:00 and 24:00~UTC), but at other hours by allowing a time shift. Therefore, instead of looking for analogues at a 24h time step, they are sought at the time step matching the predictor temporal resolution (Fig. \ref{fig:principle}). The ERA-20C dataset made here possible to test an MTW with a 12h, 6h, or 3h time step (named respectively 12h-MTW, 6h-MTW, 3h-MTW hereafter). Thus, the candidates are 2 (12h-MTW), 4 (6h-MTW), or 8 (3h-MTW) times as many (even though they are not fully independent) as in the conventional approach.

	The target situations and their corresponding observed precipitation values do not change. We then aim at predicting the exact same time series for the MTW and the conventional approach, so that the performance scores can be directly compared. In order to assess the benefit of searching for analogue situations at a sub-daily time step for quantitative precipitation prediction, an appropriate precipitation series is required. On the basis of high temporal resolution time series (Sect. \ref{sec:data}), 24h totals were processed at time steps matching the MTW by means of a moving 24h total on the period 1982-2010.

@@

	The AMs were applied to both ERA-20C and MERRA-2 datasets. Most results are presented for the ERA-20C dataset, as it allows testing a 3h-MTW, but would lead to similar conclusions with MERRA-2. The impact of an MTW was assessed on two different basis:
	\begin{itemize}
		\item Original parameters: The AMs were initially calibrated for each station based on the classic 24-hr approach. Then, the MTW was introduced into the AMs, but the parameters (spatial windows and number of analogues) were not reassessed. The analogy is the same and thus initial analogue dates should be found in the new distribution, along with new dates provided by the MTW.
		\item Recalibrated: The parameters of the AMs were reassessed after the introduction of the MTW at different time steps. Indeed, one can assume that the introduction of the MTW might change the optimum value of some parameters (different spatial windows and number of analogues). The calibration (see Sect. \ref{sec:calibration}) was then be reprocessed to adapt the AMs to the new information available through the MTW. The main difference was the increase of the optimal number of analogues, which is discussed in Sect. \ref{sec:increase_analognb}.
	\end{itemize}

	The MTW is expected to have an impact on both the selection of analogue dates and the prediction skill. Both will be analyzed separately hereafter.

@@

	First, the impact of the MTW on the selection of analogue dates is analyzed, independently of any precipitation data. This was done on the period 1982-2010, but could have been done on a longer period, as no sub-daily precipitation series is required at this stage. The results are presented for the Ulrichen station, but are very similar for all other stations. The original parameters were used here when assessing the impact of the MTW, no recalibration of the parameters took place.

@@

	When searching for analogues in the first level of analogy, such as on the geopotential heights in the 2Z method (Sect. \ref{sec:analog_method}), there are up to eight times as many candidates (even though not fully independent) with the MTW than before (Sect. \ref{sec:mtw}). Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions, for target dates over the whole period, of the analogy criterion (S1) for the $1^{st}$, $15^{th}$, and $30^{th}$ analogue rank, due to introduction of an MTW with a 12h, 6h, or 3h time step. The shape of the distributions of the conventional approach and the MTWs were found to be similar, but the values of the analogy criterion were gradually reduced (shifted to the left) with smaller time steps MTWs and were, therefore, better. The circulation analogy seems to improve regularly with the doubling of the MTW time steps. For analogues with higher ranks (e.g. $15^{th}$ or $30^{th}$), the difference between the two distributions was larger than for the first rank, which means that the improvement increased with the rank of the analogues.

	The improvements of the analogy with the rank of the analogues are summarized in Fig. \ref{fig:changes_S1}, which shows (top) quantiles of the S1 criterion for the conventional method and the MTWs at different time steps, and (bottom) quantiles of the relative reduction (meaning improvement) due to the MTWs. This confirms that all quantiles were similarly reduced (S1 distributions keep their shape), and that this improvement was constantly increasing from the first to the last analogue (Fig. \ref{fig:changes_S1} bottom). This increase in improvement with the analogue rank can be explained by the accumulation of better analogues in the selection, with new better situations pushing previous analogues to higher ranks. One can also see the regularity of the improvements brought by decreasing time steps. The introduction of the MTW allows finding better analogue situations in the first level of analogy, resulting in a selection of days with better similarity in atmospheric circulation. Moreover, this improvement is superior for MTWs with a smaller time step.

@@

	The effect of the MTW on the S1 criterion has been decomposed per season and is presented in Fig. \ref{fig:changes_S1_seasons}. Differences between the seasons are substantial, with greater improvements for winter than summer. An analysis of the selected hours for the geopotential height predictor was then performed for the MTW with different time steps (Fig. \ref{fig:hours_selection_per_season}). It was found that the new choice of the temporal window in winter, when using the MTW approach, is more balanced between the different hours of the day (more regular repartition), and this for all time steps. This means a change in selection of a greater part of the analogue dates compared to the conventional approach. On the contrary, the days during the summer months had a preference for the initial temporal window (Z500 24~h \& Z1000 12~h), likely due to more pronounced diurnal effects, which reduced the potential for improvement of the criteria. This effect is in phase with the daily cycle, and good analogues are essentially found for the same hours. When a 3h-MTW is used, the time step following the initial temporal window (so Z500 27~h \& Z1000 15~h) is almost as often selected for all seasons. However, it can be considered as relatively similar in terms of the solar influence. The other seasons were between these two extremes, which is consistent with their respective improvements.

@@

	The criteria values (RMSE) of the second level of analogy (moisture variables) were not improved by the MTW, as the number of candidates was not higher (still the $N_{1}$ days selected in the first level of analogy). The use of an MTW does not increase the sample size in this case, the second level of analogy only subsamples in the dates provided by the first level. However, this result of a globally null improvement of the RMSE values does not mean that the 2Z-2MI method cannot be improved by the MTW. It means that after the selection of the analogue situations for the synoptic circulation, the new candidate dates did not provide better analogues in terms of moisture. However, the selected dates have changed in the first level of analogy and also in the final selection, and thus the distributions of precipitation values were different.

	\subsection{Impact of the MTW on the prediction skill}
	\label{sec:influence_scores}

	The change in the performance score (CRPS) of the precipitation prediction are provided in Fig. \ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI} for the 2Z and 2Z-2MI methods, respectively. The AMs were here recalibrated on the CP, and assessed on the independent VP. The score was processed for each station and both reanalysis datasets. For ERA-20C, the 12h-MTW, 6h-MTW, and 3h-MTW could be assessed, while only the two first could be processed with the MERRA-2 dataset.

	The MTW improves the precipitation prediction, as at least from a 6h-MTW the CRPS decreases for all stations, both on the CP and the VP. The VP shows a greater variability, likely related to the short period it represents (6 yr). The prediction skill on the CP is almost always improved further by reducing the time step of the MTW, but not of the same magnitude. For ERA-20C, the magnitude of the improvement of 2Z on the CP is relatively reduced when using a 3h-MTW instead of a 6h-MTW, and the variablility on the VP increases. However, as it was shown in Fig. \ref{fig:changes_S1}, the distribution of analogue dates was improved relatively equally for every reduction of the MTW time step. A possible explanation could be that the AMs rely on the geopotential at 500~hPa, while the ERA-20C dataset was build by only assimilating surface observations. Thus, the timing of the atmospheric circulation at higher pressure levels might not be completely in phase with the real perturbation systems that are linked with the observed precipitations. The MTW with the MERRA-2 dataset and the 2Z method also shows a certain slope break after the 12h-MTW, that could not be explained, and that is less important for the 2Z-2MI method. However, the 12h-MTW shows an important variability for the 2Z-2MI method and the MERRA-2 dataset. Based on these results, the use of ERA-20C seems to be a better choice in order to apply an MTW, at least for the studied region.

	The introduction of an MTW was previously found to show greater improvement of the S1 criterion for days with higher precipitation values (Sect. \ref{sec:changes_analogy_circul}). The impact of the MTW was then assessed in terms of change of prediction skill, on the whole period, per precipitation classes (for the target day). Figure \ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, using the original parameters with the MTW. It shows that, after the introduction of the MTW, the performance score was in average further improved (reduced CRPS) for days with higher precipitation than for non-rainy days and small precipitation values. When recalibrating the parameters using the MTW, the spread of the changes in CRPS tended to decrease, but with a slight loss in performance for the most rainy days.

	Reliability diagrams were also performed on the VP for both the 2Z and 2Z-2MI methods and for the exceedence of percentiles 80~\% (P80 -- 4~mm), 90~\% (P90 -- 9.5~mm), and 95~\% (P95 -- 17.5~mm) at the Ulrichen station (Fig. \ref{fig:reliability_diagrams}). Reliability diagrams plot the observed frequency against the predicted probability of a binary event -- a threshold exceedence in our case.	For perfectly calibrated predictions, the curve should be as close as possible to the diagonal. The VP only contains six years (Sect. \ref{sec:data_methods}), and thus higher variability is present for higher thresholds, the curves being smoother and closer to the diagonals for the CP, which is longer. Figure \ref{fig:reliability_diagrams} shows that the MTW improved the reliability for both 2Z and 2Z-2MI methods and for all thresholds, as the curves move toward the diagonal with a decreasing MTW time step. For P80, the 3h-MTW predictions fits very well the observations. When considering higher thresholds, the 2Z-2MI method is generall better than 2Z. The case of a P95 threshold shows a conditional dry bias associated with larger forecast probabilities for the considered AMs, which is however substantially reduced by the 3h-MTW. This conditional dry bias means here that the AM did not predict the event with a probability equal to 1 for example for 2Z. Obtaining a probability of 1 would mean that all analogue dates for a certain target date would be above the threshold. As the number of analogue dates is 30 in this case, it becomes less likely to have 30 values above the threshold when it increases. This issue is the topic of an ongoing work. However, as one can see in Figure \ref{fig:reliability_diagrams}e\&d, the introduction of an MTW, especially with a 3h timse step, improves partly this missmatch.

@@

	When recalibrating the AMs with MTWs of different time steps, the optimal number of analogues changed for both 2Z and 2Z-2MI methods. $N_{1}$ and $N_{2}$, from the first and the second level of analogy, tend to significantly increase with the reduction of the time step of the MTW (Fig. \ref{fig:analog_nb}). When using ERA-20C, all optimal numbers of analogues (for the different analogy levels) tend in average to double when using a 6h-MTW instead of the classic approach, and to even triple when using a 3h-MTW. These higher numbers of analogues were objectivel chosen by the calibration procedure (Sect. \ref{sec:calibration}) in order to increase the prediction skill of the methods.

	A higher number of analogues generally means, with an archive of fixed length, a poorer analogy. Indeed, when the choice of the predictors or the parameters are improved, leading to a better prediction, the optimal number of analogue situations decreases. However, when the length of the archive increases, the optimal number of analogues increases too for a better performance up to a certain threshold \citep[][]{Bontron2004, Hamill2006a}. The observed increase in the number of analogue situations with the MTW resulted in better performance skills for the given methods, as it can be seen as an inflation of the archive. However, if new relevant predictors were added to the method, the number of analogues would then decrease.

>>>>

	The Analogue method (AM) is based on the hypothesis that two relatively similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}. It is a statistical downscaling methods \citep[see][for other methods]{Maraun2010} and consist of finding past situations that are similar to the target day of interest in terms of the atmospheric circulation or other synoptic predictors. The local weather variables of interest (predictand) that were observed at the analogue dates are used to construct a probabilistic prediction for the target day \citep{Duband1970, Zorita1999}. Multiple variations of the method exist \citep[a non-exhaustive listing can be found in][]{BenDaoud2016}. The AMs are used for operational precipitation forecasting, either in the context of weather forecasting, flood forecasting, or hydropower production \citep[e.g.,][]{Bontron2005, Hamill2006, Desaint2008a, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012, Obled2014, Hamill2015, BenDaoud2016}, as well as for precipitation downscaling from a climate perspective \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015}. AMs can provide multivariate predictions that are physically consistent \citep{Raynaud2016b}. Their spatial transferability is analysed in \citet{Chardon2014} and \citet{Radanovics2013}. Their temporal transferability has also been the topic of recent studies for past or future climates \citep{Dayon2015, Caillouet2016}.

	The method requires two different archives. The first is a meteorological archive describing the state of the atmosphere at a synoptic scale, such as reanalysis datasets. The second is an archive of the target variable to be predicted, here precipitation. It is most often made of daily precipitation totals at a target station or integrated over a target catchment. Obviously, the period to be used is limited to the smallest period common to the two archives.

@@

	One can question the interest of using moving daily totals when for example 6-hourly precipitation series can be predicted instead. However, the 6-hourly time series generated by the AM might not represent accurately the intra-daily precipitation distribution or variability. In addition, sometimes a resolution finer than the daily time step is not needed and another disaggregation technique may be used afterwards. Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact on 24h totals than 6h totals.

	The MTW finds analogue situations at different hours of the day, which can also be seen as an inflation of the archive length. However, despite having $x$ time more candidate situations, the quantity of new information is not expected to be as important as an $x$ time longer archive due to significant correlation between successive situations within the same day. Nevertheless, if the MTW can improve the prediction skill of the AM, it means that it does extract new information from the archive.

@@

	Synoptic-scale variables, used as predictors, were extracted from two of the most recent global reanalysis datasets: the european ERA-20C \citep{Poli2016} with a 3h temporal resolution and a spatial resolution of 1\textdegree, and MERRA-2 from NASA with a 6h temporal resolution and a spatial resolution of 0.625\textdegree x 0.5\textdegree. The study was originally performed on the NCEP/NCAR reanalysis 1 dataset \citep{Kalnay1996}, and the conclusions were similar. ERA-20C is build by assimilating only surface observations, and is thus available on a long period (1900\textendash 2010). On the contrary, MERRA-2 is build by assimilating observations at higher levels and from more sensors, including satellite data, but is then more limited in time (1980\textendash present). It is of interest to assess the relevance of an MTW with these two datasets, as they represent different kind of products. The specific advantages of ERA-20C is that it allows testing an MTW with a 3h time step, and it covers a long period. On the other hand, MERRA-2 has a higher spatial resolution and can be expected to be more accurate at higher levels of the atmosphere. The variables extracted from these datasets were geopotential heights at 500~hPa (Z500) and 1000~hPa (Z1000), as well as the total precipitable water (TPW) and the relative humidity at 850~hPa (RH850).

@@

	The first considered AM is based on the analogy of the atmospheric circulation only \citep[Table \ref{table:method_2Z};][]{Obled2002, Bontron2005}. Searching for analogue situations to a target day starts by a seasonal stratification through a preselection step of the potential candidates for analogy. The restriction is a search for analogue days within a 4-month window centred on the target date for every year of the archive. The similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score (S1) that is a comparison of gradients on geopotential heights over a certain spatial window and at certain hours:

@@

	The second reference method \citep[2Z-2MI, Table \ref{table:method_2Z-2MI};][]{Bontron2005} adds a subsequent level of analogy with moisture variables, compared by means of the root-mean-square error (RMSE):

@@

	AMs rely on parameters that need to be defined for every level of analogy. Here, the selection of the meteorological variables used as predictors, as well as their corresponding analogy criteria, pressure level, and hour of the day, were considered identical to the methods 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) described above. The parameters that were here calibrated are:

@@

	The semi-automatic sequential procedure elaborated by \citet{Bontron2004} was used to calibrate the AM \cite[see also][]{Radanovics2013, BenDaoud2016}. The analogy levels (e.g. the atmospheric circulation or moisture index) are calibrated sequentially. The parameters calibrated by this approach, for every level of analogy, are the spatial windows on which the predictors are compared and the number of analogues. The procedure, as defined by \citet{Bontron2004}, consists of the following steps:

	\begin{enumerate}
		\item For every level of analogy:
		\begin{enumerate}
			\item Identification of the most skilled unitary cell (one point for moisture variables and four for geopotential heights in order to process the gradients) over a large domain. Every point (or cell) of the full domain is assessed on all predictors of the level of analogy, jointly (consisting generally of the same variable but on different pressure levels and at different hours).
			\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain. The spatial window grows until no improvement is reached.
			\item The number of analogue situations $N_{1}$, which was initially set at an arbitrary value, is then reconsidered and optimized for the current level of analogy.
		\end{enumerate}
		\item A new level of analogy can then be added, based on other variables (such as the moisture index) at chosen pressure levels and hours of the day. The number of analogues for the next level of analogy, $N_{2}$, is initiated at a chosen value. The procedure starts again from step 1 (calibration of the spatial window and the number of analogues) for the new level. The parameters calibrated on the previous analogy levels are fixed and do not change. 
		\item Finally, the numbers of analogues $N_{1}$ and $N_{2}$ for the different levels of analogy are reassessed. This is done iteratively by varying the number of analogues of each level in a systematic way.
	\end{enumerate}

@@

	The 29-yr hourly precipitation dataset was divided into a calibration period (CP) and a validation period (VP) in order to assess the robustness of the proposed improvements on independent data. The selection of the VP was evenly distributed over the entire series \citep{BenDaoud2010} to reduce potential biases related to trends linked to climate change or to the evolution in measurement techniques. Thus, one out of every five years was selected for validation, which represents a total of 6~yr for the VP and 23~yr for the CP.

@@

	The moving time window (MTW) technique aims at finding better analogue situations at different hours of the day rather than comparing the predictors at the same fixed hours. The target situation (the day to predict) is still the same as in the conventional approach, that is a daily precipitation total between 06:00 and 30:00~UTC, characterized by predictors which are here Z1000 and Z500 at 12:00 and 24:00~UTC respectively. The difference is that candidate situations are not only considered at the same time (12:00 and 24:00~UTC), but at other hours by allowing a time shift. Therefore, instead of looking for analogues at a 24h time step, they are sought at the time step matching the predictor temporal resolution (Fig. \ref{fig:principle}). The ERA-20C dataset made here possible to test an MTW with a 12h, 6h, or 3h time step (named respectively 12h-MTW, 6h-MTW, 3h-MTW hereafter). Thus, the candidates are 2 (12h-MTW), 4 (6h-MTW), or 8 (3h-MTW) times as many (even though they are not fully independent) as in the conventional approach.

	The target situations and their corresponding observed precipitation values do not change. We then aim at predicting the exact same time series for the MTW and the conventional approach, so that the performance scores can be directly compared. In order to assess the benefit of searching for analogue situations at a sub-daily time step for quantitative precipitation prediction, an appropriate precipitation series is required. On the basis of hourly time series (Sect. \ref{sec:data}), 24h totals were processed at time steps matching the MTW by means of a moving 24h total on the period 1982-2010.

@@

	The AMs were applied to both ERA-20C and MERRA-2 datasets. Most results are presented for the ERA-20C dataset, as it allows testing a 3h-MTW, but would lead to similar conclusions with MERRA-2. The impact of an MTW was assessed on two different basis:
	\begin{itemize}
		\item Original parameters: The AMs were initially calibrated for each station based on the conventional 24h approach. Then, the MTW was introduced into the AMs, but the parameters (spatial windows and number of analogues) were not reassessed. The analogy was then identical, with the only difference that the MTW had more candidate at disposal.
		\item Recalibrated: The parameters of the AMs were reassessed after the introduction of the MTW at different time steps. Indeed, one can assume that the introduction of the MTW might change the optimum value of some parameters (different spatial windows and number of analogues). The calibration (Sect. \ref{sec:calibration}) was then be reprocessed to adapt the AMs to the new information available through the MTW. The main difference was the increase in the optimal number of analogues, which is discussed in Sect. \ref{sec:increase_analognb}.
	\end{itemize}

	The MTW is expected to have an impact on both the selection of analogue dates and the prediction skill. Both are analyzed separately hereafter.

@@

	First, the impact of the MTW on the selection of analogue dates was analyzed, independently of any precipitation data. This was done on the period 1982-2010, but could have been done on a longer period, as no sub-daily precipitation series is required at this stage. The results are presented for the Ulrichen station, but were very similar for all other stations. The original parameters were used here when assessing the impact of the MTW, no recalibration of the parameters took place.

@@

	When searching for analogues in the first level of analogy, such as on the geopotential heights in the 2Z method (Sect. \ref{sec:analog_method}), there were up to eight times as many candidates (even though not fully independent) with the MTW than before (Sect. \ref{sec:mtw}). Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions, for target dates over the CP, of the analogy criterion (S1) for the $1^{st}$, $15^{th}$, and $30^{th}$ analogue rank, due to introduction of an MTW with a 12h, 6h, or 3h time step. The shape of the distributions of the conventional approach and the MTWs were found to be similar, but the values of the analogy criterion were gradually reduced (shifted to the left) with smaller time steps MTWs and were, therefore, better. The circulation analogy was here regularly improved with the doubling of the MTW time step. For analogues with higher ranks (e.g. $15^{th}$ or $30^{th}$), the difference between the two distributions was larger than for the first rank, which means that the improvement increased with the rank of the analogues.

	The improvements of the analogy with the rank of the analogues are summarized in Fig. \ref{fig:changes_S1}, which shows (top) quantiles of the S1 criterion for the conventional method and the MTWs at different time steps, and (bottom) quantiles of the relative reduction (meaning improvement) due to the MTWs. This confirms that this improvement is constantly increasing from the first to the last analogue (Fig. \ref{fig:changes_S1} bottom). It can be explained by the accumulation of better analogues in the selection, with new better situations pushing previous analogues to higher ranks. One can also see the regularity of the improvements brought by decreasing time steps. The introduction of the MTW allows finding better analogue situations in the first level of analogy, resulting in a selection of days with here a better similarity in the atmospheric circulation. This improvement is superior for MTWs with a smaller time step.

@@

	The effect of the MTW on the S1 criterion has been decomposed per season and is presented in Fig. \ref{fig:changes_S1_seasons}. Differences between the seasons are substantial, with greater improvements for winter than summer. An analysis of the selected hours for the geopotential height predictor was then performed for the MTW with different time steps (Fig. \ref{fig:hours_selection_per_season}). It was found that the new choice of the temporal window in winter is more balanced between the different hours of the day (more regular repartition), and this for all MTW time steps. This means a change in selection of a greater portion of the analogue dates compared to the conventional approach. On the contrary, the days in summer had a preference for the initial temporal window (Z500 24~h \& Z1000 12~h). It is likely due to more pronounced diurnal effects, which reduced the potential for improvement of the criteria. These effects are in phase with the daily cycle, and good analogues were essentially found for the same hours. When a 3h-MTW was used, the time step following the initial temporal window (so Z500 27~h \& Z1000 15~h) was almost as often selected as the initial one for all seasons. It can be considered as relatively similar in terms of the solar influence. The other seasons were between these two extremes, which is consistent with their respective improvements in S1.

@@

	These criterion values were not improved by the MTW because the number of candidates was not higher (still the $N_{1}$ days selected in the first level of analogy). The use of an MTW did not increase the sample size in this case, as the second level of analogy only subsamples in the dates provided by the first level. However, this result of a globally null improvement of the RMSE values does not mean that the 2Z-2MI method cannot be improved by the MTW. It means that after the selection of the analogue dates for the synoptic circulation, the new candidate dates did not provide better analogues in terms of moisture. However, the selected dates have changed in the first level of analogy and also in the final selection, and thus the distributions of precipitation values were different, which can have an impact on the performance of the precipitation prediction.

	\subsection{Impact of the MTW on the precipitation prediction}
	\label{sec:influence_scores}

	The changes in the performance score (CRPS) of the precipitation prediction are provided in Fig. \ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI} for the 2Z and 2Z-2MI methods, respectively. The AMs were here recalibrated on the CP, and assessed on the independent VP. The score was processed for each station and both reanalysis datasets. For ERA-20C, the 12h-MTW, 6h-MTW, and 3h-MTW could be assessed, while only the two first could be processed with the MERRA-2 dataset.

	The MTW improved the precipitation prediction, as the CRPS globally decreased for all stations, both on the CP and the VP. The VP showed a greater variability, likely related to the short period it represents (6 yr). The prediction skill on the CP was almost always improved further by reducing the time step of the MTW, but not of the same magnitude. For ERA-20C, the magnitude of the improvement of 2Z on the CP was relatively reduced when using a 3h-MTW instead of a 6h-MTW, and the variablility on the VP increased. However, as it was shown in Fig. \ref{fig:changes_S1}, the selection of analogue dates was improved relatively equally for every reduction of the MTW time step. A possible reason could be that the ERA-20C dataset was build by only assimilating surface observations, while the AMs rely on the geopotential at 500~hPa. Thus, the timing of the atmospheric circulation at higher pressure levels might not be completely in phase with the real perturbation systems that caused the observed precipitations. The MTW with the MERRA-2 dataset and the 2Z method also showed a certain slope break after the 12h-MTW, that could not be explained, and that is less important for the 2Z-2MI method. However, the 12h-MTW resulted in important variability for the 2Z-2MI method and the MERRA-2 dataset.

	The introduction of an MTW was previously found to show greater improvement of the S1 criterion for days with higher precipitation values (Sect. \ref{sec:changes_analogy_circul}). The impact of the MTW was then assessed in terms of change of prediction performance per precipitation classes (for the target day). Figure \ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, using the original parameters with the MTW. It shows that, after the introduction of the MTW, the performance score was in average further improved (reduced CRPS) for days with higher precipitation than for non-rainy days and small precipitation values. When recalibrating the parameters using the MTW, the spread of the changes in CRPS tended to decrease, but with a slight loss in performance for the most rainy days (not shown).

	Reliability diagrams were also performed on the VP for both the 2Z and 2Z-2MI methods and for the exceedence of percentiles 80~\% (P80 -- 4~mm), 90~\% (P90 -- 9.5~mm), and 95~\% (P95 -- 17.5~mm) at the Ulrichen station (Fig. \ref{fig:reliability_diagrams}). Reliability diagrams plot the observed frequency against the predicted probability of a binary event -- a threshold exceedence in this case. For perfectly calibrated predictions, the curve should be as close as possible to the diagonal. The VP only contains six years (Sect. \ref{sec:data_methods}), and thus higher variability is present for higher thresholds, the curves being smoother and closer to the diagonals for the CP, which is longer (not shown). Figure \ref{fig:reliability_diagrams} shows that the MTW improved the reliability for both 2Z and 2Z-2MI methods and for all thresholds, as the curves moved toward the diagonal with a decreasing MTW time step. For P80, the 3h-MTW predictions fited very well the observed frequency. When considering higher thresholds, the 2Z-2MI method is generally better than 2Z. The case of a P95 threshold shows a conditional dry bias associated with larger forecast probabilities for the considered AMs, which was however substantially reduced by the 3h-MTW. This conditional dry bias means for example here that the AM did not predict the event with a probability equal to 1 for 2Z. Obtaining a predicted probability of exceedence of 1 would mean that all analogue dates for a certain target date would be above the threshold. As the number of analogue dates is 30 in this case, it becomes less likely to have 30 values above the threshold when it increases. This issue is the topic of an ongoing work. However, as one can see in Figure \ref{fig:reliability_diagrams} (bottom), the introduction of an MTW, especially with a 3h timse step, improves partly this missmatch.

@@

	When recalibrating the AMs with MTWs of different time steps, the optimal number of analogues changed for both 2Z and 2Z-2MI methods. $N_{1}$ and $N_{2}$, from the first and the second level of analogy, tend to significantly increase with the reduction of the time step of the MTW (Fig. \ref{fig:analog_nb}). When using ERA-20C, all optimal numbers of analogues (for the different analogy levels) tend in average to double when using a 6h-MTW instead of the classic approach, and to even triple when using a 3h-MTW. These higher numbers of analogues were objectively chosen by the calibration procedure (Sect. \ref{sec:calibration}) in order to increase the prediction skill of the methods.
